\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Penalizing LSTM Output Size for Risk Control in Stock Market Technical Analysis\\
}

\author{\IEEEauthorblockN{Franklin Doane}
\IEEEauthorblockA{\textit{dept. of Computer Science} \\
\textit{Tennessee Technological University}\\
Cookeville, United States \\
doanefranklin89@gmail.edu}
}

\maketitle

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

\section{Introduction}

\section{Related work}

Other work has been done to use LSTMs for stock market prediction. Mei Sun, Pegiuang Lang, 

\subsection{LSTMs with market analysis}
\subsection{Using }


\section{Significance of using size penalty}
\section{Size penalty significance over time}



\section{Results}
\section{Conclusion}
\section{Limitations}

\begin{thebibliography}{00}
\bibitem{b1} M. Sun, Q. Li, and P. Lin, “Short-term stock price forecasting based on an SVD-LSTM model,” Intelligent Automation \& Soft Computing, vol. 28, no. 2, pp. 369–378, Feb. 2021, doi: https://doi.org/10.32604/iasc.2021.014962.
\bibitem{b2} Q. Li, N. Kamaruddin, S. S. Yuhaniz, and H. A. A. Al-Jaifi, “Forecasting stock prices changes using long-short term memory neural network with symbolic genetic programming,” Scientific Reports, vol. 14, no. 1, p. 422, Jan. 2024, doi: https://doi.org/10.1038/s41598-023-50783-0.
\bibitem{b3} H. Jiang, X. Hu, and H. Jia, “Penalized logistic regressions with technical indicators predict up and down trends,” Soft Computing, Aug. 2022, doi: https://doi.org/10.1007/s00500-022-07404-1.
\end{thebibliography}


\end{document}
